14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-03-24 rules/rules19.tex
Made a pass on the sat/unsat/all/24 sec scores.  I introduced a difference between performance (parallel/sequential) and score (the sat/unsat/all/24 stuff).  I hope you like it, and that it's not overly complicated...

A solver's \emph{raw score} for each benchmark is a quadruple $\langle
e, n, w, c\rangle$, with $e \in \{0, 1\}$ the number of erroneous
results (usually~$e = 0$), $0 \leq n \leq N$ the number of correct
results,\footnote{Here, $N$ is the number of \akey{check-sat} commands
  in the benchmark.  Recall that single problem track benchmarks have just one
  \akey{check-sat} command; incremental track benchmarks may have
  multiple \akey{check-sat} commands.} $w \in [0,T]$ the (real-valued)
wall-clock time in seconds, and $c \in [0, 4T]$ the (real-valued) CPU
time in seconds, measured across all cores and sub-processes, until
the solver process terminates.

@@

\rem{TODO: 24s, sat, unsat score description}

SMT-COMP has traditionally emphasized sequential performance (i.e.,
CPU time) over parallel performance (i.e., wall-clock time).  StarExec
measures both, and we intend to recognize both best sequential and
best parallel solvers in all competitive single problem track divisions.

The raw score, as defined in Section~\ref{sec:benchmark-scoring},
favors parallel solvers, which may utilize all available processor
cores.  To evaluate sequential performance, we derive a
\emph{sequential score} by imposing a (virtual) CPU time limit equal
to the wall-clock time limit~$T$.  A solver result is taken into
consideration for the sequential score only if the solver process
terminates within this CPU time limit.  More specifically, for a given
raw score $\langle e, n, w, c\rangle$, the corresponding sequential
score is defined as~$\langle e_S, n_S, c_S\rangle$, where
\begin{itemize}
\item $e_S = 0$ and $n_S = 0$ if $c > T$, $e_S = e$ and $n_S = n$
  otherwise,
\item $c_S = \min\ \{c, T\}$.\footnote{\emph{Rationale:} Under this
  score, a solver should not benefit from using multiple processor
  cores.  Conceptually, the sequential score should be (nearly)
  unchanged if the solver was run on a single-core processor, up to a
  time limit of~$T$.}
\end{itemize}

@@

\header{Single Problem Track: Removal of Disagreements.}
%
Before division scores are computed for the Single Problem Track, benchmarks
with unknown status are removed from the competition results if two
(or more) solvers that are sound on benchmarks with known status
disagree on their result.  More specifically, a solver (including a
solver that was entered into the competition by the organizers for
comparison purposes) is \emph{sound on benchmarks with known status}
for a division if its raw score (Section~\ref{sec:benchmark-scoring})
is of the form $\langle 0, n, w, c\rangle$ for each benchmark in the
division, i.e., if it did not produce any erroneous results.  Two
solvers \emph{disagree} on a benchmark if one of them reported
\texttt{sat} and the other reported \texttt{unsat}.  Only the
remaining benchmarks are used in the following computation of division
scores (but the organizers may report disagreements for informational
purposes).

@@

To compute a solver's score for a division, the solver's individual
benchmark scores for all benchmarks in the division are first
multiplied by a scalar weight that depends on the benchmark's family,
and then summed component-wise.

@@

For Single Problem Track and unsat-core track divisions, we will separately
compute the weighted sum of all raw scores
(Section~\ref{sec:benchmark-scoring}) $$\sum_b \alpha'_b \cdot \langle
e_b \cdot N, n_b \cdot N, w_b, c_b\rangle$$ where the sum is over all
benchmarks in the division to assess parallel performance, and the
weighted sum of all sequential scores (Section~\ref{sec:sequential})
to assess sequential performance.  For incremental track divisions,
division scores will be based on raw scores only.\footnote{Since
  incremental track benchmarks may be partially solved, defining a
  useful sequential score for the incremental track would require
  information not provided by the raw score, e.g., detailed timing
  information for each result.}

Division scores are compared lexicographically:
\begin{itemize}
\item A weighted sum of raw scores $\langle e, n, w, c\rangle$ is
  better than $\langle e', n', w', c'\rangle$ iff $e < e'$ or ($e =
  e'$ and $n > n'$) or ($e = e'$ and $n = n'$ and $w < w'$) or ($e =
  e'$ and $n = n'$ and $w = w'$ and $c < c'$).  That is, fewer errors
  takes precedence over more correct solutions, which takes precedence
  over less wall-clock time taken, which takes precedence over less
  CPU time taken.
\item A weighted sum of sequential scores $\langle e_S, n_S,
  c_S\rangle$ is better than $\langle e_S', n_S', c_S'\rangle$ iff
  $e_S < e_S'$ or ($e_S = e_S'$ and $n_S > n_S'$) or ($e_S = e_S'$ and
  $n_S = n_S'$ and $c_S < c_S'$).  That is, fewer errors takes
  precedence over more correct solutions, which takes precedence over
  less CPU time taken.
\end{itemize}
%
We will not make any comparisons between raw scores and sequential
scores, as these are intended to measure fundamentally different
performance characteristics.

@@

>>>>

A solver's \emph{parallel performance} for each benchmark is a quadruple $\langle
e, n, w, c\rangle$, with $e \in \{0, 1\}$ the number of erroneous
results (usually~$e = 0$), $0 \leq n \leq N$ the number of correct
results,\footnote{Here, $N$ is the number of \akey{check-sat} commands
  in the benchmark.  Recall that single problem track benchmarks have just one
  \akey{check-sat} command; incremental track benchmarks may have
  multiple \akey{check-sat} commands.} $w \in [0,T]$ the (real-valued)
wall-clock time in seconds, and $c \in [0, 4T]$ the (real-valued) CPU
time in seconds, measured across all cores and sub-processes, until
the solver process terminates.

@@

\iffalse
SMT-COMP has traditionally emphasized sequential performance (i.e.,
CPU time) over parallel performance (i.e., wall-clock time).  StarExec
measures both, and we intend to recognize both best sequential and
best parallel solvers in all competitive single problem track divisions.
\fi

The parallel performance, as defined in Section~\ref{sec:benchmark-scoring},
favors parallel solvers, which may utilize all available processor
cores.  To evaluate sequential performance, we derive a
\emph{sequential performance} by imposing a (virtual) CPU time limit equal
to the wall-clock time limit~$T$.  A solver result is taken into
consideration for the sequential performance only if the solver process
terminates within this CPU time limit.  More specifically, for a given
parallel performance $\langle e, n, w, c\rangle$, the corresponding sequential
performance is defined as~$\langle e_S, n_S, c_S\rangle$, where
\begin{itemize}
\item $e_S = 0$ and $n_S = 0$ if $c > T$, $e_S = e$ and $n_S = n$
  otherwise,
\item $c_S = \min\ \{c, T\}$.\footnote{\emph{Rationale:} Under this
  measure, a solver should not benefit from using multiple processor
  cores.  Conceptually, the sequential performance should be (nearly)
  unchanged if the solver was run on a single-core processor, up to a
  time limit of~$T$.}
\end{itemize}

@@

We compute in total eight different {\em scores} for each division based
on solvers' parallel and sequential performance.  The two performances
are computed separately for {\em all}, {\em satisfiable}, and {\em
unsatisfiable instances}.  In addition we compute the performances for a
\emph{one-minute wonder} track, where each solver is run with a
24-second timeout.

\header{Single Problem Track: Removal of Disagreements.}
%
Before division scores are computed for the Single Problem Track, benchmarks
with unknown status are removed from the competition results if two
(or more) solvers that are sound on benchmarks with known status
disagree on their result.  More specifically, a solver (including a
solver that was entered into the competition by the organizers for
comparison purposes) is \emph{sound on benchmarks with known status}
for a division if its parallel performance (Section~\ref{sec:benchmark-scoring})
is of the form $\langle 0, n, w, c\rangle$ for each benchmark in the
division, i.e., if it did not produce any erroneous results.  Two
solvers \emph{disagree} on a benchmark if one of them reported
\texttt{sat} and the other reported \texttt{unsat}.  Only the
remaining benchmarks are used in the following computation of division
scores (but the organizers may report disagreements for informational
purposes).

@@

To compute a solver's scores for a division, the solver's individual
benchmark scores for all benchmarks in the division are first
multiplied by a scalar weight that depends on the benchmark's family,
and then summed component-wise.

@@

For Single Problem Track and unsat-core track divisions, we will separately
compute the weighted sum of all benchmarks separately based on the
parallel performance and sequential performance.
(Section~\ref{sec:benchmark-scoring})
%
These will be computed as
$$\sum_b \alpha'_b \cdot \langle e_b \cdot N, n_b \cdot N, w_b, c_b\rangle$$
%
where the sum $\sum_b$ ranges over all parallel performances when
computing parallel performance scores, and over all sequential
performances when computing sequential performance scores.
\iffalse
benchmarks in the division to assess parallel performance, and the
weighted sum of all sequential performances (Section~\ref{sec:sequential})
to assess sequential performance.
\fi
For incremental track divisions,
division scores will be based on parallel performance only.\footnote{Since
  incremental track benchmarks may be partially solved, defining a
  useful sequential performance for the incremental track would require
  information not provided by the parallel performance, e.g., detailed timing
  information for each result.}

Division scores are compared lexicographically:
\begin{itemize}
\item A weighted sum of parallel performances $\langle e, n, w, c\rangle$ is
  better than $\langle e', n', w', c'\rangle$ iff $e < e'$ or ($e =
  e'$ and $n > n'$) or ($e = e'$ and $n = n'$ and $w < w'$) or ($e =
  e'$ and $n = n'$ and $w = w'$ and $c < c'$).  That is, fewer errors
  takes precedence over more correct solutions, which takes precedence
  over less wall-clock time taken, which takes precedence over less
  CPU time taken.
\item A weighted sum of sequential performances $\langle e_S, n_S,
  c_S\rangle$ is better than $\langle e_S', n_S', c_S'\rangle$ iff
  $e_S < e_S'$ or ($e_S = e_S'$ and $n_S > n_S'$) or ($e_S = e_S'$ and
  $n_S = n_S'$ and $c_S < c_S'$).  That is, fewer errors takes
  precedence over more correct solutions, which takes precedence over
  less CPU time taken.
\end{itemize}
%
We will not make any comparisons between parallel and sequential
performances, as these are intended to measure fundamentally different
performance characteristics.

@@

\rem{TODO: Shall we drop the competition-wide scoring?}
